The Second Data Release of the INT Photometric H$\alpha$ Survey of the Northern Galactic Plane (IPHAS DR2)

### 2014-06-30 paper/iphas-dr2-rev1.tex
Initial commit of paper revision

\documentclass[a4paper,useAMS,usenatbib]{mn2e}
\pdfpagewidth=\paperwidth
\pdfpageheight=\paperheight
\usepackage{amssymb,amsmath}
\usepackage[pdftex]{graphicx}
\usepackage{longtable} 
\usepackage{float}
\usepackage{booktabs}
\usepackage{aas_macros}
\usepackage{caption}
\usepackage{subcaption}

%\voffset=-0.5in

@@

@@

\footnotesize{
  \bibliographystyle{mn2e}
  \bibliography{iphas-dr2-arxiv}
}

>>>>

% This is revision 1 of the IPHAS DR2 paper,
% created in response to the referee comments received on 24 June 2014
\documentclass[a4paper,useAMS,usenatbib]{mn2e}
\pdfpagewidth=\paperwidth
\pdfpageheight=\paperheight
\usepackage{amssymb,amsmath}
\usepackage[pdftex]{graphicx}
\usepackage{longtable} 
\usepackage{float}
\usepackage{booktabs}
\usepackage{aas_macros}
\usepackage{caption}
\usepackage{subcaption}

@@

\begin{table}
    \caption{Overview of the key survey properties.}
    \label{tbl:survey}
    \begin{center}
        \begin{tabular}{ll}
        \toprule
        Property & Value \\
        \midrule
        Telescope & 2.5m Isaac Newton Telescope, La Palma \\
        Instrument & Wide Field Camera \\
        FoV CCD & ... \\
        Dates & ... \\
        Detector scale & 0.33 arcsec/pixel \\
        Filters & $r$, $i$, \ha \\
        Filter properties & See Table~2 \\
        Exposure time & 30~s ($r$), 10~s ($i$), 120~s (\ha) \\
        Magnitude limit (5$\sigma$, Vega) & 21.3 ($r$), 20.1 ($i$), 20.3 (\ha) \\
        PSF FWHM (median) & 1.1\arcsec\ ($r$), 1.0\arcsec\ ($i$), 1.1\arcsec\ (\ha) \\
        Survey area & $\sim 1860$~deg$^2$ \\
        Footprint limits & $ -5\degr < b < +5\degr,\ 29\degr < \ell < 215\degr$ \\
        \bottomrule
        \end{tabular}
	\end{center}
\end{table}

@@

\footnotesize{
  \bibliographystyle{mn2e}
  \bibliography{iphas-dr2}
}
